---
title: "Sirin_2011"
author: "Grace Pang"
date: "2023-02-02"
output:
  html_document:
    code_folding: show
    toc: yes
    toc_float: yes
    theme: flatly
  pdf_document:
    toc: yes
editor_options:
  markdown:
    wrap: 72
---

TRYING OUT WITH HYDROMAD 


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE) 
```

# Setup 
## Load data packages
```{r library}
library(tidyverse) # manipulate & plot data
library(car) # data analysis
library(emmeans) # descriptive stats
library(lme4) # mixed effects models
library(lmerTest) # to get p-values from mixed effects models
library("readxl") # read excel 
library(ggthemes) # colour palettes
library (ggeffects) # plotting estimated marginal means 
library(MuMIn) #for model selection 
library(vegan) #nmds

library(ggrepel) #for adding labels on my plot  

# CORRECTIONS 
# Packages
library(tidyverse) # manipulate & plot data
library(car) # data analysis
library(emmeans) # descriptive stats
library(lme4) # mixed effects models
library(lmerTest) # to get p-values from mixed effects models

# "Make it pretty" set up
library(patchwork) # to organise plots
library(gghalves) # raincloud plot :)

## Custom colour palettes :)
library(ggthemes) 
library(ggsci)
library(ghibli)

    library(tidyverse) # manipulate & plot data
    library(dplyr)
    library(car) # data analysis
    library(emmeans) # descriptive stats
    library(gghalves) # raincloud plot :)
    
    library("ggpubr") # for stats test

library(lubridate) # for converting date / date time tihngs 

#HYDROLOGY 
library("hydroTSM") 
library(lattice)
library(zoo) 
library(IETD) #inter-event time definition

# HYDROMAD 
library(zoo)
library(latticeExtra)
library(polynom)
library(Hmisc)
library(reshape)
require(devtools) 
library(remotes)
# install_github("josephguillaume/hydromad")

library(package = "hydromad")
help("hydromad")
library(openxlsx) #to save to excel

```


Identifying eventseq
https://hydromad.catchment.org/man/eventseq.html from https://hydromad.catchment.org/#eventseq
```{r Sequence}
data(Queanbeyan)
## wet period
x <- window(Queanbeyan, start = "1974-01-01", end = "1976-12-01")

evp <- eventseq(x$P, thresh = 5, inthresh = 1, indur = 4, continue = TRUE) 
#x$P is the zoo of date and ppt , threshold = value must be above 5 // inthresh = when events stop after the first threshold // indur = sereis must remain below th einthresh for this many time steps in order to stop an event // continue = TRUE to extend each event until following event, 
#evp= zoo, with daily date.time. and evp. 
evq <- eventseq(x$Q, thresh = 2, indur = 4, mingap = 5)
#	mingap: the minimum number of time steps that can separate events. Any inter-event durations shorter than this will be subsumed into the surrounding event.

nlevels(evp) ## number of events
nlevels(evq)
str(evq)
table(coredata(evq))
eventapply(x$Q, evq, FUN = sum)
eventapply(x, evq, FUN = mean)
eventinfo(x$Q, evq)

evplot <- xyplot(x) + 
  layer_(panel.xblocks(evp, col = c("grey90", "grey80"), border = "grey80")) +
  layer(panel.xblocks(evq, block.y = 0, vjust = 1, col = 1))
evplot

update(evplot, type = "s",
    xlim = as.Date(c("1990-07-01", "1990-08-31"))) +
  layer(panel.abline(h = c(5,1), lty = 2), packets = 1)

## example of requesting a threshold giving about 'n' events
set.seed(0)
ee <- eventseq(rnorm(100), n = 10, mingap = 2)
nlevels(ee)
attr(ee, "thresh")




```

## 
## example of classifying events based on hydro properties
##
```{r}
data(Queanbeyan)
x <- window(Queanbeyan, start = "1974-01-01", end = "1976-12-01")
e <- eventseq(x$P, thresh = 5, inthresh = 1, indur = 4, continue = TRUE)


## classify events based on max flow
qclass <- cut(ave(coredata(x$Q), coredata(e), FUN = max),
              c(0, 0.5, 1, Inf))
qclass <- zoo(qclass, time(x))

## Classify events based on antecedent flow
x <- merge(x, Q1 = lag(x$Q, 1), all = c(TRUE, FALSE))
head1 <- function(z) z[1]
q1class <- cut(ave(coredata(x$Q1), coredata(e), FUN = head1),
               c(0, 0.2, 0.3, Inf))
q1class <- zoo(q1class, time(x))

## combined classification
combin <- factor(paste("M", unclass(qclass), "_A", unclass(q1class), sep =""))
combin <- zoo(combin, time(x))

## check results
head(data.frame(x, event = unclass(e), qclass, q1class, combin), 50)

## number of events in each class
each.e <- !duplicated(e)
table(coredata(combin[each.e]))
```


[EH like not needed]
Testing out the tutorial here 
https://hydromad.catchment.org/downloads/tutorial.pdf
```{r}
data1 <-  data(Cotter)
data1

#To plot the raw (daily) time series:
xyplot(Cotter)
#To plot a section of the time series:
xyplot(window(Cotter, start = "1974-01-01", end = "1975-01-01"))
# time series aggregated to a monthly time step:
 monthlyPQE <- aggregate(Cotter, as.yearmon, mean)
 xyplot(monthlyPQE, screens = c("Streamflow (mm/day)",
"Areal rain (mm/day)", "Temperature (deg. C)"),
xlab = NULL)
```


Testing out on my work 

```{r iRL: loading docs}
SGR100_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.1_S_evaporation_GR100.xls")
str(SGR100_ev)
head(SGR100_ev)

# W3.2_S_GR50.xls
SGR50_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.2_S_evaporation_GR50.xls")
str(SGR50_ev)
head(SGR50_ev)

Snone_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.0_S_evaporation_NONE.xls")
str(Snone_ev)
head(Snone_ev)

SGRPP100_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.7_S_evaporation_GRPP100.xls")
str(SGRPP100_ev)
head(SGRPP100_ev)

SGRPP50_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.8_S_evaporation_GRPP50.xls")
str(SGRPP50_ev)
head(SGRPP50_ev)


SPP100_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.3_S_evaporation_PP100.xls")
str(SPP100_ev)
head(SPP100_ev)

SPP50_ev<- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.4_S_evaporation_PP50.xls")
str(SPP50_ev)
head(SPP50_ev)

SRG100_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.5_S_evaporation_RG50.xls")
str(SRG100_ev)
head(SRG100_ev)

SRG50_ev <- read_excel("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/9 Output data/W4_excel_Sirin_yearly_evaporation/4.5_S_evaporation_RG100.xls")
str(SRG50_ev)
head(SRG50_ev)
```

Converting to class zoo

```{r}
dfSnone_ev <- data.frame(Snone_ev$`Date/Time`, Snone_ev$Rainfall, Snone_ev$`Total inflow`)
zSnone_ev <- read.zoo(dfSnone_ev)
class(zSnone_ev)
head(zSnone_ev)
```
TRYING OUT ON MY DATASET!! 
!! data= Snone_ev
// rainhigh event + hours duration 
// rainlow event + hour duration 

progress check 
/ ok, got the number of events. 
/ BUT idk how to proceed... 
```{r Trying out on my dataset}
rainhigh <- eventseq(zSnone_ev$Snone_ev.Rainfall, 
                     thresh = 10, inthresh = 9, indur = 2, mingap = 6)
nlevels(rainhigh) #number of events 
str(rainhigh)
table(coredata(rainhigh)) #coredata extract the core data
#df$date <- as.Date(df$date, origin="2020-01-01")
#convert to df with 

rainlow <- eventseq(zSnone_ev$Snone_ev.Rainfall, thresh = 1, indur = 2, mingap = 6)
nlevels(rainlow) #number of events 
str(rainlow)
table(coredata(rainlow))

#eventapply(x$Q, evq, FUN = sum)
eventapply(Snone_ev$Rainfall, rainhigh, FUN = sum)
```

Getting the runoff reduction for the high rainfall event
- probably gg to hard code it... 

OUTPUTS
// event_highrain_SRG50_ev x7, changing Snone_ev... : contains event datetime, duration, event rain, event outflow 
// COMBINED TABLE: event_highrain_ALL
// HIGH RAIN REDUCTION BY EACH NBS: reduction_highrain


```{r Getting event outflow for each scenario for the high rainfall event }
#UNIVERSAL 
rainhigh11events <- Snone_ev %>% 
    filter(Rainfall>=10) %>% 
    arrange(desc(Rainfall))  %>% 
    slice(1,4,7,10,13,16,19,22,25,28,29)
# Getting the data/time and hours for the table set up 
rainhigh10events <- Snone_ev %>% 
    filter(Rainfall>=10) %>% 
    arrange(desc(Rainfall))  %>% 
    slice(1,4,7,10,13,19,22,25,29,28) %>% 
    select(`Date/Time`) %>% 
    mutate(Hours=c(7,4,4,4,4,4,4,4,4,2))

#SPECIFIC 
#SNONE_EV 
  #Scenario: Filtering out relevant rows for summing later 
  a <- Snone_ev %>% 
    slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
  #Scenario: Getting the specific Rainfall and outflow for scenario
  b <- data.frame (
    EventRainfall_mm=c(sum(a$Rainfall[1:7]) , sum(a$Rainfall[8:11]), sum(a$Rainfall[12:15]), sum(a$Rainfall[16:19]), sum(a$Rainfall[20:23]), sum(a$Rainfall[24:27]), sum(a$Rainfall[28:31]), sum(a$Rainfall[32:35]), sum(a$Rainfall[36:39]), sum(a$Rainfall[40:41])), 
    NoNBSOutflow_mms=c(sum(a$`Total inflow`[1:7]) , sum(a$`Total inflow`[8:11]), sum(a$`Total inflow`[12:15]), sum(a$`Total inflow`[16:19]), sum(a$`Total inflow`[20:23]), sum(a$`Total inflow`[24:27]), sum(a$`Total inflow`[28:31]), sum(a$`Total inflow`[32:35]), sum(a$`Total inflow`[36:39]), sum(a$`Total inflow`[40:41])))
  #Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
  event_highrain <- cbind(rainhigh10events, b)
  event_highrain
  
#SGR100_ev
  #Scenario: Filtering out relevant rows for summing later 
  a_SGR100_ev <- SGR100_ev %>% 
    slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
  #Scenario: Getting the specific Rainfall and outflow for scenario
  b_SGR100_ev <- data.frame (
    EventRainfall_mm=c(sum(a_SGR100_ev$Rainfall[1:7]) , sum(a_SGR100_ev$Rainfall[8:11]), sum(a_SGR100_ev$Rainfall[12:15]), sum(a_SGR100_ev$Rainfall[16:19]), sum(a_SGR100_ev$Rainfall[20:23]), sum(a_SGR100_ev$Rainfall[24:27]), sum(a_SGR100_ev$Rainfall[28:31]), sum(a_SGR100_ev$Rainfall[32:35]), sum(a_SGR100_ev$Rainfall[36:39]), sum(a_SGR100_ev$Rainfall[40:41])), 
    EventOutflow_mms=c(sum(a_SGR100_ev$`Total inflow`[1:7]) , sum(a_SGR100_ev$`Total inflow`[8:11]), sum(a_SGR100_ev$`Total inflow`[12:15]), sum(a_SGR100_ev$`Total inflow`[16:19]), sum(a_SGR100_ev$`Total inflow`[20:23]), sum(a_SGR100_ev$`Total inflow`[24:27]), sum(a_SGR100_ev$`Total inflow`[28:31]), sum(a_SGR100_ev$`Total inflow`[32:35]), sum(a_SGR100_ev$`Total inflow`[36:39]), sum(a_SGR100_ev$`Total inflow`[40:41])))
  #Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
  event_highrain_SGR100_ev <- cbind(rainhigh10events, b_SGR100_ev)
  event_highrain_SGR100_ev


#SGR50_ev
#Scenario: Filtering out relevant rows for summing later 
a_SGR50_ev <- SGR50_ev %>% 
  slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
#Scenario: Getting the specific Rainfall and outflow for scenario
b_SGR50_ev <- data.frame (
  EventRainfall_mm=c(sum(a_SGR50_ev$Rainfall[1:7]) , sum(a_SGR50_ev$Rainfall[8:11]), sum(a_SGR50_ev$Rainfall[12:15]), sum(a_SGR50_ev$Rainfall[16:19]), sum(a_SGR50_ev$Rainfall[20:23]), sum(a_SGR50_ev$Rainfall[24:27]), sum(a_SGR50_ev$Rainfall[28:31]), sum(a_SGR50_ev$Rainfall[32:35]), sum(a_SGR50_ev$Rainfall[36:39]), sum(a_SGR50_ev$Rainfall[40:41])), 
  EventOutflow_mms=c(sum(a_SGR50_ev$`Total inflow`[1:7]) , sum(a_SGR50_ev$`Total inflow`[8:11]), sum(a_SGR50_ev$`Total inflow`[12:15]), sum(a_SGR50_ev$`Total inflow`[16:19]), sum(a_SGR50_ev$`Total inflow`[20:23]), sum(a_SGR50_ev$`Total inflow`[24:27]), sum(a_SGR50_ev$`Total inflow`[28:31]), sum(a_SGR50_ev$`Total inflow`[32:35]), sum(a_SGR50_ev$`Total inflow`[36:39]), sum(a_SGR50_ev$`Total inflow`[40:41])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_highrain_SGR50_ev <- cbind(rainhigh10events, b_SGR50_ev)
event_highrain_SGR50_ev
  

#SGRPP100_ev
#Scenario: Filtering out relevant rows for summing later 
a_SGRPP100_ev <- SGRPP100_ev %>% 
  slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
#Scenario: Getting the specific Rainfall and outflow for scenario
b_SGRPP100_ev <- data.frame (
  EventRainfall_mm=c(sum(a_SGRPP100_ev$Rainfall[1:7]) , sum(a_SGRPP100_ev$Rainfall[8:11]), sum(a_SGRPP100_ev$Rainfall[12:15]), sum(a_SGRPP100_ev$Rainfall[16:19]), sum(a_SGRPP100_ev$Rainfall[20:23]), sum(a_SGRPP100_ev$Rainfall[24:27]), sum(a_SGRPP100_ev$Rainfall[28:31]), sum(a_SGRPP100_ev$Rainfall[32:35]), sum(a_SGRPP100_ev$Rainfall[36:39]), sum(a_SGRPP100_ev$Rainfall[40:41])), 
  EventOutflow_mms=c(sum(a_SGRPP100_ev$`Total inflow`[1:7]) , sum(a_SGRPP100_ev$`Total inflow`[8:11]), sum(a_SGRPP100_ev$`Total inflow`[12:15]), sum(a_SGRPP100_ev$`Total inflow`[16:19]), sum(a_SGRPP100_ev$`Total inflow`[20:23]), sum(a_SGRPP100_ev$`Total inflow`[24:27]), sum(a_SGRPP100_ev$`Total inflow`[28:31]), sum(a_SGRPP100_ev$`Total inflow`[32:35]), sum(a_SGRPP100_ev$`Total inflow`[36:39]), sum(a_SGRPP100_ev$`Total inflow`[40:41])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_highrain_SGRPP100_ev <- cbind(rainhigh10events, b_SGRPP100_ev)
event_highrain_SGRPP100_ev

#SGRPP50_ev
#Scenario: Filtering out relevant rows for summing later 
a_SGRPP50_ev <- SGRPP50_ev %>% 
  slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
#Scenario: Getting the specific Rainfall and outflow for scenario
b_SGRPP50_ev <- data.frame (
  EventRainfall_mm=c(sum(a_SGRPP50_ev$Rainfall[1:7]) , sum(a_SGRPP50_ev$Rainfall[8:11]), sum(a_SGRPP50_ev$Rainfall[12:15]), sum(a_SGRPP50_ev$Rainfall[16:19]), sum(a_SGRPP50_ev$Rainfall[20:23]), sum(a_SGRPP50_ev$Rainfall[24:27]), sum(a_SGRPP50_ev$Rainfall[28:31]), sum(a_SGRPP50_ev$Rainfall[32:35]), sum(a_SGRPP50_ev$Rainfall[36:39]), sum(a_SGRPP50_ev$Rainfall[40:41])), 
  EventOutflow_mms=c(sum(a_SGRPP50_ev$`Total inflow`[1:7]) , sum(a_SGRPP50_ev$`Total inflow`[8:11]), sum(a_SGRPP50_ev$`Total inflow`[12:15]), sum(a_SGRPP50_ev$`Total inflow`[16:19]), sum(a_SGRPP50_ev$`Total inflow`[20:23]), sum(a_SGRPP50_ev$`Total inflow`[24:27]), sum(a_SGRPP50_ev$`Total inflow`[28:31]), sum(a_SGRPP50_ev$`Total inflow`[32:35]), sum(a_SGRPP50_ev$`Total inflow`[36:39]), sum(a_SGRPP50_ev$`Total inflow`[40:41])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_highrain_SGRPP50_ev <- cbind(rainhigh10events, b_SGRPP50_ev)
event_highrain_SGRPP50_ev


#SPP100_ev
#Scenario: Filtering out relevant rows for summing later 
a_SPP100_ev <- SPP100_ev %>% 
  slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
#Scenario: Getting the specific Rainfall and outflow for scenario
b_SPP100_ev <- data.frame (
  EventRainfall_mm=c(sum(a_SPP100_ev$Rainfall[1:7]) , sum(a_SPP100_ev$Rainfall[8:11]), sum(a_SPP100_ev$Rainfall[12:15]), sum(a_SPP100_ev$Rainfall[16:19]), sum(a_SPP100_ev$Rainfall[20:23]), sum(a_SPP100_ev$Rainfall[24:27]), sum(a_SPP100_ev$Rainfall[28:31]), sum(a_SPP100_ev$Rainfall[32:35]), sum(a_SPP100_ev$Rainfall[36:39]), sum(a_SPP100_ev$Rainfall[40:41])), 
  EventOutflow_mms=c(sum(a_SPP100_ev$`Total inflow`[1:7]) , sum(a_SPP100_ev$`Total inflow`[8:11]), sum(a_SPP100_ev$`Total inflow`[12:15]), sum(a_SPP100_ev$`Total inflow`[16:19]), sum(a_SPP100_ev$`Total inflow`[20:23]), sum(a_SPP100_ev$`Total inflow`[24:27]), sum(a_SPP100_ev$`Total inflow`[28:31]), sum(a_SPP100_ev$`Total inflow`[32:35]), sum(a_SPP100_ev$`Total inflow`[36:39]), sum(a_SPP100_ev$`Total inflow`[40:41])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_highrain_SPP100_ev <- cbind(rainhigh10events, b_SPP100_ev)
event_highrain_SPP100_ev

#SPP50_ev
#Scenario: Filtering out relevant rows for summing later 
a_SPP50_ev <- SPP50_ev %>% 
  slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
#Scenario: Getting the specific Rainfall and outflow for scenario
b_SPP50_ev <- data.frame (
  EventRainfall_mm=c(sum(a_SPP50_ev$Rainfall[1:7]) , sum(a_SPP50_ev$Rainfall[8:11]), sum(a_SPP50_ev$Rainfall[12:15]), sum(a_SPP50_ev$Rainfall[16:19]), sum(a_SPP50_ev$Rainfall[20:23]), sum(a_SPP50_ev$Rainfall[24:27]), sum(a_SPP50_ev$Rainfall[28:31]), sum(a_SPP50_ev$Rainfall[32:35]), sum(a_SPP50_ev$Rainfall[36:39]), sum(a_SPP50_ev$Rainfall[40:41])), 
  EventOutflow_mms=c(sum(a_SPP50_ev$`Total inflow`[1:7]) , sum(a_SPP50_ev$`Total inflow`[8:11]), sum(a_SPP50_ev$`Total inflow`[12:15]), sum(a_SPP50_ev$`Total inflow`[16:19]), sum(a_SPP50_ev$`Total inflow`[20:23]), sum(a_SPP50_ev$`Total inflow`[24:27]), sum(a_SPP50_ev$`Total inflow`[28:31]), sum(a_SPP50_ev$`Total inflow`[32:35]), sum(a_SPP50_ev$`Total inflow`[36:39]), sum(a_SPP50_ev$`Total inflow`[40:41])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_highrain_SPP50_ev <- cbind(rainhigh10events, b_SPP50_ev)
event_highrain_SPP50_ev

#SRG100_ev
#Scenario: Filtering out relevant rows for summing later 
a_SRG100_ev <- SRG100_ev %>% 
  slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
#Scenario: Getting the specific Rainfall and outflow for scenario
b_SRG100_ev <- data.frame (
  EventRainfall_mm=c(sum(a_SRG100_ev$Rainfall[1:7]) , sum(a_SRG100_ev$Rainfall[8:11]), sum(a_SRG100_ev$Rainfall[12:15]), sum(a_SRG100_ev$Rainfall[16:19]), sum(a_SRG100_ev$Rainfall[20:23]), sum(a_SRG100_ev$Rainfall[24:27]), sum(a_SRG100_ev$Rainfall[28:31]), sum(a_SRG100_ev$Rainfall[32:35]), sum(a_SRG100_ev$Rainfall[36:39]), sum(a_SRG100_ev$Rainfall[40:41])), 
  EventOutflow_mms=c(sum(a_SRG100_ev$`Total inflow`[1:7]) , sum(a_SRG100_ev$`Total inflow`[8:11]), sum(a_SRG100_ev$`Total inflow`[12:15]), sum(a_SRG100_ev$`Total inflow`[16:19]), sum(a_SRG100_ev$`Total inflow`[20:23]), sum(a_SRG100_ev$`Total inflow`[24:27]), sum(a_SRG100_ev$`Total inflow`[28:31]), sum(a_SRG100_ev$`Total inflow`[32:35]), sum(a_SRG100_ev$`Total inflow`[36:39]), sum(a_SRG100_ev$`Total inflow`[40:41])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_highrain_SRG100_ev <- cbind(rainhigh10events, b_SRG100_ev)
event_highrain_SRG100_ev

#SRG50_ev
#Scenario: Filtering out relevant rows for summing later 
a_SRG50_ev <- SRG50_ev %>% 
  slice(4344:4350, 1950:1953, 2979:2982, 3222:3225, 4965:4968, 5730:5733, 3771:3774, 5901:5904, 6864:6867, 6727:6728) 
#Scenario: Getting the specific Rainfall and outflow for scenario
b_SRG50_ev <- data.frame (
  EventRainfall_mm=c(sum(a_SRG50_ev$Rainfall[1:7]) , sum(a_SRG50_ev$Rainfall[8:11]), sum(a_SRG50_ev$Rainfall[12:15]), sum(a_SRG50_ev$Rainfall[16:19]), sum(a_SRG50_ev$Rainfall[20:23]), sum(a_SRG50_ev$Rainfall[24:27]), sum(a_SRG50_ev$Rainfall[28:31]), sum(a_SRG50_ev$Rainfall[32:35]), sum(a_SRG50_ev$Rainfall[36:39]), sum(a_SRG50_ev$Rainfall[40:41])), 
  EventOutflow_mms=c(sum(a_SRG50_ev$`Total inflow`[1:7]) , sum(a_SRG50_ev$`Total inflow`[8:11]), sum(a_SRG50_ev$`Total inflow`[12:15]), sum(a_SRG50_ev$`Total inflow`[16:19]), sum(a_SRG50_ev$`Total inflow`[20:23]), sum(a_SRG50_ev$`Total inflow`[24:27]), sum(a_SRG50_ev$`Total inflow`[28:31]), sum(a_SRG50_ev$`Total inflow`[32:35]), sum(a_SRG50_ev$`Total inflow`[36:39]), sum(a_SRG50_ev$`Total inflow`[40:41])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_highrain_SRG50_ev <- cbind(rainhigh10events, b_SRG50_ev)
event_highrain_SRG50_ev


#Combining the event outflows 
event_highrain_ALL <- event_highrain %>% 
  mutate(GR100_Outflow= event_highrain_SGR100_ev$EventOutflow_mms, 
         GR50_Outflow= event_highrain_SGR50_ev$EventOutflow_mms, 
         PP100_Outflow= event_highrain_SPP100_ev$EventOutflow_mms, 
         PP50_Outflow= event_highrain_SPP50_ev$EventOutflow_mms, 
         RG100_Outflow= event_highrain_SRG100_ev$EventOutflow_mms, 
         RG50_Outflow= event_highrain_SRG50_ev$EventOutflow_mms, 
         GRPP100_Outflow= event_highrain_SGRPP100_ev$EventOutflow_mms, 
         GRPP50_Outflow= event_highrain_SGRPP50_ev$EventOutflow_mms)
# CONVERTING to EXCEL
setwd("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/10 R coding/FYP_timeseries/Table_outputs")
write.xlsx(event_highrain_ALL, "raw_highrain_Sirin", rowNames = FALSE)

#Finding the reduction% 
reduction_highrain <- event_highrain_ALL %>% 
  mutate(
         R_GR100 = (NoNBSOutflow_mms- GR100_Outflow)/NoNBSOutflow_mms*100 ,
         R_GR50 = (NoNBSOutflow_mms- GR50_Outflow)/NoNBSOutflow_mms*100, 
         R_PP100 = (NoNBSOutflow_mms- PP100_Outflow)/NoNBSOutflow_mms*100,
         R_PP50= (NoNBSOutflow_mms- PP50_Outflow)/NoNBSOutflow_mms*100, 
         R_RG100 = (NoNBSOutflow_mms- RG100_Outflow)/NoNBSOutflow_mms*100, 
         R_RG50= (NoNBSOutflow_mms- RG50_Outflow)/NoNBSOutflow_mms*100, 
         R_GRPP100 = (NoNBSOutflow_mms- GRPP100_Outflow)/NoNBSOutflow_mms*100, 
         R_GRPP50 = (NoNBSOutflow_mms- GRPP50_Outflow)/NoNBSOutflow_mms*100)

reduction_highrain <- reduction_highrain %>% select (-c('GR100_Outflow', 'GR50_Outflow', 'PP100_Outflow', 'PP50_Outflow', 'RG100_Outflow', 'RG50_Outflow', 'GRPP100_Outflow', 'GRPP50_Outflow'))

reduction_highrain
# CONVERTING TABLES TO CSV TO WORD 
setwd("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/10 R coding/FYP_timeseries/Table_outputs")
write.xlsx(reduction_highrain, "reduction_highrain_Sirin", rowNames = FALSE)
```


Low rainfall evnet 
#SGR100_ev
#SGR50_ev
  
#SGRPP100_ev
  
#SGRPP50_ev
  
#SPP100_ev
  
#SPP50_ev

#SRG100_ev
  
#SRG50_ev


```{r Low rainfall event }
rainlowevents <- Snone_ev %>% 
  slice(3981,1347,1482, 6018,6351,6624,6844,2856,3165,4671) %>% #slice all teh rain event start date time 
  select(`Date/Time`) %>% 
  mutate(Hours=c(13,7,7,7,7,7,5,4,4,4))

#SPECIFIC 
#SNONE_EV 
#Scenario: Filtering out relevant rows for summing later 
c <- Snone_ev %>% 
    slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d <- data.frame (
    EventRainfall_mm=c(sum(c$Rainfall[1:13]) , sum(c$Rainfall[14:20]), sum(c$Rainfall[21:27]), sum(c$Rainfall[28:34]), sum(c$Rainfall[35:41]), sum(c$Rainfall[42:48]), sum(c$Rainfall[49:53]), sum(c$Rainfall[54:57]), sum(c$Rainfall[58:61]), sum(c$Rainfall[62:65])), 
    NoNBSOutflow_mms=c(sum(c$`Total inflow`[1:13]) , sum(c$`Total inflow`[14:20]), sum(c$`Total inflow`[21:27]), sum(c$`Total inflow`[28:34]), sum(c$`Total inflow`[35:41]), sum(c$`Total inflow`[42:48]), sum(c$`Total inflow`[49:53]), sum(c$`Total inflow`[54:57]), sum(c$`Total inflow`[58:61]), sum(c$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
  event_lowrain <- cbind(rainlowevents, d)
  event_lowrain
  
#SGR100_ev
c_SGR100_ev <- SGR100_ev %>% 
    slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SGR100_ev <- data.frame (
    EventRainfall_mm=c(sum(c_SGR100_ev$Rainfall[1:13]) , sum(c_SGR100_ev$Rainfall[14:20]), sum(c_SGR100_ev$Rainfall[21:27]), sum(c_SGR100_ev$Rainfall[28:34]), sum(c_SGR100_ev$Rainfall[35:41]), sum(c_SGR100_ev$Rainfall[42:48]), sum(c_SGR100_ev$Rainfall[49:53]), sum(c_SGR100_ev$Rainfall[54:57]), sum(c_SGR100_ev$Rainfall[58:61]), sum(c_SGR100_ev$Rainfall[62:65])), 
    EventOutflow_mms=c(sum(c_SGR100_ev$`Total inflow`[1:13]) , sum(c_SGR100_ev$`Total inflow`[14:20]), sum(c_SGR100_ev$`Total inflow`[21:27]), sum(c_SGR100_ev$`Total inflow`[28:34]), sum(c_SGR100_ev$`Total inflow`[35:41]), sum(c_SGR100_ev$`Total inflow`[42:48]), sum(c_SGR100_ev$`Total inflow`[49:53]), sum(c_SGR100_ev$`Total inflow`[54:57]), sum(c_SGR100_ev$`Total inflow`[58:61]), sum(c_SGR100_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
  event_lowrain_SGR100_ev <- cbind(rainlowevents, d_SGR100_ev)
  event_lowrain_SGR100_ev
  

#SGR50_ev
c_SGR50_ev <- SGR50_ev %>% 
  slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SGR50_ev <- data.frame (
  EventRainfall_mm=c(sum(c_SGR50_ev$Rainfall[1:13]) , sum(c_SGR50_ev$Rainfall[14:20]), sum(c_SGR50_ev$Rainfall[21:27]), sum(c_SGR50_ev$Rainfall[28:34]), sum(c_SGR50_ev$Rainfall[35:41]), sum(c_SGR50_ev$Rainfall[42:48]), sum(c_SGR50_ev$Rainfall[49:53]), sum(c_SGR50_ev$Rainfall[54:57]), sum(c_SGR50_ev$Rainfall[58:61]), sum(c_SGR50_ev$Rainfall[62:65])), 
  EventOutflow_mms=c(sum(c_SGR50_ev$`Total inflow`[1:13]) , sum(c_SGR50_ev$`Total inflow`[14:20]), sum(c_SGR50_ev$`Total inflow`[21:27]), sum(c_SGR50_ev$`Total inflow`[28:34]), sum(c_SGR50_ev$`Total inflow`[35:41]), sum(c_SGR50_ev$`Total inflow`[42:48]), sum(c_SGR50_ev$`Total inflow`[49:53]), sum(c_SGR50_ev$`Total inflow`[54:57]), sum(c_SGR50_ev$`Total inflow`[58:61]), sum(c_SGR50_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_lowrain_SGR50_ev <- cbind(rainlowevents, d_SGR50_ev)
event_lowrain_SGR50_ev


#SGRPP100_ev
c_SGRPP100_ev <- SGRPP100_ev %>% 
  slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SGRPP100_ev <- data.frame (
  EventRainfall_mm=c(sum(c_SGRPP100_ev$Rainfall[1:13]) , sum(c_SGRPP100_ev$Rainfall[14:20]), sum(c_SGRPP100_ev$Rainfall[21:27]), sum(c_SGRPP100_ev$Rainfall[28:34]), sum(c_SGRPP100_ev$Rainfall[35:41]), sum(c_SGRPP100_ev$Rainfall[42:48]), sum(c_SGRPP100_ev$Rainfall[49:53]), sum(c_SGRPP100_ev$Rainfall[54:57]), sum(c_SGRPP100_ev$Rainfall[58:61]), sum(c_SGRPP100_ev$Rainfall[62:65])), 
  EventOutflow_mms=c(sum(c_SGRPP100_ev$`Total inflow`[1:13]) , sum(c_SGRPP100_ev$`Total inflow`[14:20]), sum(c_SGRPP100_ev$`Total inflow`[21:27]), sum(c_SGRPP100_ev$`Total inflow`[28:34]), sum(c_SGRPP100_ev$`Total inflow`[35:41]), sum(c_SGRPP100_ev$`Total inflow`[42:48]), sum(c_SGRPP100_ev$`Total inflow`[49:53]), sum(c_SGRPP100_ev$`Total inflow`[54:57]), sum(c_SGRPP100_ev$`Total inflow`[58:61]), sum(c_SGRPP100_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_lowrain_SGRPP100_ev <- cbind(rainlowevents, d_SGRPP100_ev)
event_lowrain_SGRPP100_ev
  

#SGRPP50_ev
c_SGRPP50_ev <- SGRPP50_ev %>% 
  slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SGRPP50_ev <- data.frame (
  EventRainfall_mm=c(sum(c_SGRPP50_ev$Rainfall[1:13]) , sum(c_SGRPP50_ev$Rainfall[14:20]), sum(c_SGRPP50_ev$Rainfall[21:27]), sum(c_SGRPP50_ev$Rainfall[28:34]), sum(c_SGRPP50_ev$Rainfall[35:41]), sum(c_SGRPP50_ev$Rainfall[42:48]), sum(c_SGRPP50_ev$Rainfall[49:53]), sum(c_SGRPP50_ev$Rainfall[54:57]), sum(c_SGRPP50_ev$Rainfall[58:61]), sum(c_SGRPP50_ev$Rainfall[62:65])), 
  EventOutflow_mms=c(sum(c_SGRPP50_ev$`Total inflow`[1:13]) , sum(c_SGRPP50_ev$`Total inflow`[14:20]), sum(c_SGRPP50_ev$`Total inflow`[21:27]), sum(c_SGRPP50_ev$`Total inflow`[28:34]), sum(c_SGRPP50_ev$`Total inflow`[35:41]), sum(c_SGRPP50_ev$`Total inflow`[42:48]), sum(c_SGRPP50_ev$`Total inflow`[49:53]), sum(c_SGRPP50_ev$`Total inflow`[54:57]), sum(c_SGRPP50_ev$`Total inflow`[58:61]), sum(c_SGRPP50_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_lowrain_SGRPP50_ev <- cbind(rainlowevents, d_SGRPP50_ev)
event_lowrain_SGRPP50_ev

  
#SPP100_ev
c_SPP100_ev <- SPP100_ev %>% 
  slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SPP100_ev <- data.frame (
  EventRainfall_mm=c(sum(c_SPP100_ev$Rainfall[1:13]) , sum(c_SPP100_ev$Rainfall[14:20]), sum(c_SPP100_ev$Rainfall[21:27]), sum(c_SPP100_ev$Rainfall[28:34]), sum(c_SPP100_ev$Rainfall[35:41]), sum(c_SPP100_ev$Rainfall[42:48]), sum(c_SPP100_ev$Rainfall[49:53]), sum(c_SPP100_ev$Rainfall[54:57]), sum(c_SPP100_ev$Rainfall[58:61]), sum(c_SPP100_ev$Rainfall[62:65])), 
  EventOutflow_mms=c(sum(c_SPP100_ev$`Total inflow`[1:13]) , sum(c_SPP100_ev$`Total inflow`[14:20]), sum(c_SPP100_ev$`Total inflow`[21:27]), sum(c_SPP100_ev$`Total inflow`[28:34]), sum(c_SPP100_ev$`Total inflow`[35:41]), sum(c_SPP100_ev$`Total inflow`[42:48]), sum(c_SPP100_ev$`Total inflow`[49:53]), sum(c_SPP100_ev$`Total inflow`[54:57]), sum(c_SPP100_ev$`Total inflow`[58:61]), sum(c_SPP100_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_lowrain_SPP100_ev <- cbind(rainlowevents, d_SPP100_ev)
event_lowrain_SPP100_ev

  
#SPP50_ev
c_SPP50_ev <- SPP50_ev %>% 
  slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SPP50_ev <- data.frame (
  EventRainfall_mm=c(sum(c_SPP50_ev$Rainfall[1:13]) , sum(c_SPP50_ev$Rainfall[14:20]), sum(c_SPP50_ev$Rainfall[21:27]), sum(c_SPP50_ev$Rainfall[28:34]), sum(c_SPP50_ev$Rainfall[35:41]), sum(c_SPP50_ev$Rainfall[42:48]), sum(c_SPP50_ev$Rainfall[49:53]), sum(c_SPP50_ev$Rainfall[54:57]), sum(c_SPP50_ev$Rainfall[58:61]), sum(c_SPP50_ev$Rainfall[62:65])), 
  EventOutflow_mms=c(sum(c_SPP50_ev$`Total inflow`[1:13]) , sum(c_SPP50_ev$`Total inflow`[14:20]), sum(c_SPP50_ev$`Total inflow`[21:27]), sum(c_SPP50_ev$`Total inflow`[28:34]), sum(c_SPP50_ev$`Total inflow`[35:41]), sum(c_SPP50_ev$`Total inflow`[42:48]), sum(c_SPP50_ev$`Total inflow`[49:53]), sum(c_SPP50_ev$`Total inflow`[54:57]), sum(c_SPP50_ev$`Total inflow`[58:61]), sum(c_SPP50_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_lowrain_SPP50_ev <- cbind(rainlowevents, d_SPP50_ev)
event_lowrain_SPP50_ev


#SRG100_ev
c_SRG100_ev <- SRG100_ev %>% 
  slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SRG100_ev <- data.frame (
  EventRainfall_mm=c(sum(c_SRG100_ev$Rainfall[1:13]) , sum(c_SRG100_ev$Rainfall[14:20]), sum(c_SRG100_ev$Rainfall[21:27]), sum(c_SRG100_ev$Rainfall[28:34]), sum(c_SRG100_ev$Rainfall[35:41]), sum(c_SRG100_ev$Rainfall[42:48]), sum(c_SRG100_ev$Rainfall[49:53]), sum(c_SRG100_ev$Rainfall[54:57]), sum(c_SRG100_ev$Rainfall[58:61]), sum(c_SRG100_ev$Rainfall[62:65])), 
  EventOutflow_mms=c(sum(c_SRG100_ev$`Total inflow`[1:13]) , sum(c_SRG100_ev$`Total inflow`[14:20]), sum(c_SRG100_ev$`Total inflow`[21:27]), sum(c_SRG100_ev$`Total inflow`[28:34]), sum(c_SRG100_ev$`Total inflow`[35:41]), sum(c_SRG100_ev$`Total inflow`[42:48]), sum(c_SRG100_ev$`Total inflow`[49:53]), sum(c_SRG100_ev$`Total inflow`[54:57]), sum(c_SRG100_ev$`Total inflow`[58:61]), sum(c_SRG100_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_lowrain_SRG100_ev <- cbind(rainlowevents, d_SRG100_ev)
event_lowrain_SRG100_ev
  

#SRG50_ev
c_SRG50_ev <- SRG50_ev %>% 
  slice(3981:3993,1347:1353, 1482:1488,6018:6024, 6351:6357, 6624:6630, 6844:6848 , 2856:2859, 3165:3168, 4671:4674) 
#Scenario: Getting the specific Rainfall and outflow for scenario
d_SRG50_ev <- data.frame (
  EventRainfall_mm=c(sum(c_SRG50_ev$Rainfall[1:13]) , sum(c_SRG50_ev$Rainfall[14:20]), sum(c_SRG50_ev$Rainfall[21:27]), sum(c_SRG50_ev$Rainfall[28:34]), sum(c_SRG50_ev$Rainfall[35:41]), sum(c_SRG50_ev$Rainfall[42:48]), sum(c_SRG50_ev$Rainfall[49:53]), sum(c_SRG50_ev$Rainfall[54:57]), sum(c_SRG50_ev$Rainfall[58:61]), sum(c_SRG50_ev$Rainfall[62:65])), 
  EventOutflow_mms=c(sum(c_SRG50_ev$`Total inflow`[1:13]) , sum(c_SRG50_ev$`Total inflow`[14:20]), sum(c_SRG50_ev$`Total inflow`[21:27]), sum(c_SRG50_ev$`Total inflow`[28:34]), sum(c_SRG50_ev$`Total inflow`[35:41]), sum(c_SRG50_ev$`Total inflow`[42:48]), sum(c_SRG50_ev$`Total inflow`[49:53]), sum(c_SRG50_ev$`Total inflow`[54:57]), sum(c_SRG50_ev$`Total inflow`[58:61]), sum(c_SRG50_ev$`Total inflow`[62:65])))
#Scenario: Joining dataframes: of event, and sum of rainfall and outflow 
event_lowrain_SRG50_ev <- cbind(rainlowevents, d_SRG50_ev)
event_lowrain_SRG50_ev



#Combining the event outflows 
event_lowrain_ALL <- event_lowrain %>% 
  mutate(GR100_Outflow= event_lowrain_SGR100_ev$EventOutflow_mms, 
         GR50_Outflow= event_lowrain_SGR50_ev$EventOutflow_mms, 
         PP100_Outflow= event_lowrain_SPP100_ev$EventOutflow_mms, 
         PP50_Outflow= event_lowrain_SPP50_ev$EventOutflow_mms, 
         RG100_Outflow= event_lowrain_SRG100_ev$EventOutflow_mms, 
         RG50_Outflow= event_lowrain_SRG50_ev$EventOutflow_mms, 
         GRPP100_Outflow= event_lowrain_SGRPP100_ev$EventOutflow_mms, 
         GRPP50_Outflow= event_lowrain_SGRPP50_ev$EventOutflow_mms)
# CONVERTING TABLES TO EXCEL
setwd("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/10 R coding/FYP_timeseries/Table_outputs")
write.xlsx(event_lowrain_ALL, "raw_lowrain_Sirin", rowNames = FALSE)

#Finding the reduction% 
reduction_lowrain <- event_lowrain_ALL %>% mutate(
    R_GR100 = (NoNBSOutflow_mms- GR100_Outflow)/NoNBSOutflow_mms*100 ,
    R_GR50 = (NoNBSOutflow_mms- GR50_Outflow)/NoNBSOutflow_mms*100, 
    R_PP100 = (NoNBSOutflow_mms- PP100_Outflow)/NoNBSOutflow_mms*100,
    R_PP50= (NoNBSOutflow_mms- PP50_Outflow)/NoNBSOutflow_mms*100, 
    R_RG100 = (NoNBSOutflow_mms- RG100_Outflow)/NoNBSOutflow_mms*100, 
    R_RG50= (NoNBSOutflow_mms- RG50_Outflow)/NoNBSOutflow_mms*100, 
    R_GRPP100 = (NoNBSOutflow_mms- GRPP100_Outflow)/NoNBSOutflow_mms*100, 
    R_GRPP50 = (NoNBSOutflow_mms- GRPP50_Outflow)/NoNBSOutflow_mms*100)

reduction_lowrain <- reduction_lowrain %>% select (-c('GR100_Outflow', 'GR50_Outflow', 'PP100_Outflow', 'PP50_Outflow', 'RG100_Outflow', 'RG50_Outflow', 'GRPP100_Outflow', 'GRPP50_Outflow'))

reduction_lowrain
# CONVERTING TABLES TO CSV TO WORD 
setwd("/Users/gracep/Library/CloudStorage/OneDrive-NanyangTechnologicalUniversity/FYP/10 R coding/FYP_timeseries/Table_outputs")
write.xlsx(reduction_lowrain, "reduction_lowrain_Sirin", rowNames = FALSE)

reduction_lowrain
reduction_highrain
```



```{r}

```









